Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
Improve image, add RSSI to meter conversion formula

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{acronym}
\usepackage{listing-style}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes.geometric,positioning,automata,calc}
\usepackage[hidelinks]{hyperref}
\usepackage[inline]{enumitem}

@@

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations in which too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that is able to detect the distance from other simialr devices via Bluetooth.
%
For the sake of simplicity,
in the experiment we relied on smartphones to emulate wearables,
and we used \meta{
    NICOLAS please write here (within meta, so that it remains blue)
    what you used to measure the signal strenght and estimate the distance.
    Even formulas, calibration procedures, and stuff
}
%
In our case the warning was issued through a monitor,
whose color was set to tones ranging from green to red depending on the average distance among people:
the shorter the distance, the more red the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arcs lenghts represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher is the alert level
        (reddish tones).
        %
        \meta{NICOLAS riduci lo spazio vuoto fra i tre casi, così da guadagnare spazio. La legenda potrebbe essere messa sotto o sopra per guadagnarne di ulteriore}
    }
    \label{fig:crowd-alert}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{acronym}
\usepackage{listing-style}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes.geometric,positioning,automata,calc}
\usepackage[hidelinks]{hyperref}
\usepackage[inline]{enumitem}
\usepackage{siunitx}
\DeclareSIUnit{\decibelmeter}{dBm}

@@

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations in which too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that is able to detect the distance from other similar devices via Bluetooth.
%
For the sake of simplicity,
in the experiment we relied on smartphones to emulate wearables,
and we used
% \meta{
%     NICOLAS please write here (within meta, so that it remains blue)
%     what you used to measure the signal strenght and estimate the distance.
%     Even formulas, calibration procedures, and stuff
% }
%
\meta{
    the RSSI signal of the bluetooth during the scanning of the environment
    to estimate the distance between the devices.
    %
    In particular, we used the following formula to estimate the distance:
    \begin{equation*}
        d = 10^{\cfrac{(A - A')}{(10 \cdot n)}}
    \end{equation*}
    where $A$ is the RSSI value at 1 meter,
    $A'$ is the RSSI value measured by the device
    and $n$ is the path loss exponent.
    %
    Since the definition of $A'$ and $n$ is not trivial,
    and depends on the environment in which the system is deployed,
    we have calibrated the system in a test environment by measuring the RSSI signal
    at 1 meter using two smartphones.
    %
    The following values emerged from the calibration phase:
    $A=\qty{-60}{\decibelmeter}$ and $n = \qty{2.0}{\decibel}$.
}
%
In our case the warning was issued through a monitor,
whose color was set to tones ranging from green to red depending on the average distance among people:
the shorter the distance, the more red the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arcs lenghts represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher is the alert level
        (reddish tones).
        %
        \meta{NICOLAS riduci lo spazio vuoto fra i tre casi, così da guadagnare spazio. La legenda potrebbe essere messa sotto o sopra per guadagnarne di ulteriore}
    }
    \label{fig:crowd-alert}
\end{figure}
